\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}

\geometry{margin=1in}

\title{CS328 Final Project - Premise}
\date{\today}
\author{Mason Fabel - \textit{fabe0940@vandals.uidaho.edu}}

\begin{document}
\maketitle

\begin{section}{Overview}
For the final project, I would like to create a two-player 2D fighting game.
Instead of using the more traditional martial arts characters or characters from
an existing franchise, however, the characters in this game will be graduate
students of various majors, competing for research funding.
\end{section}

\begin{section}{Audience}
While there already are many fighting games with large and active fan bases, they
all share a focus on deep, competitive play and sophisticated moves and
metagames. While this is part of the draw of the fighting game genre, it makes
it difficult for new players with no experience to jump in, understand a game,
and have fun.

Thus, my game will be designed with players who do not usually play fighting
games in mind. The focus will be on simple and clear gameplay to allow new
players to understand the system and begin having fun as quickly as possible.
\end{section}

\begin{section}{Technical Details}
This game will be targeted for desktop computers only. Development will be done
in Java using LibGDX, so all major platforms should be able to run the final
product, but OSX 10.7 will be the only officially supported platform, as the
development team does not have access to other systems.

A large portion of the fun in fighting games comes from competing against other
people, and so this project will focus on creating a two player game instead
of creating a workable AI opponent. In order to facilitate this, the game will
be playable by two players on the same computer, or from two computers on the
same local area network. Furthermore, there will not be any sort of matchmaking
lobby or central server, as the game will instead rely on the user entering an
IP address to connect to by hand.

Having multiple players share a single keyboard to play a game is awkward at
best, so this game will also allow players to use a Playstation 3 controller
connected to their computer instead of the keyboard. In addition, using one
input device will not disable the other, so a player can, if they so desire,
play for a while on a controller, then use the keyboard, and then go back to
the controller, all within one match.
\end{section}

\begin{section}{Team}
This game will be developed by a team consisting of Mason Fabel.
\end{section}

\end{document}
